Tables

### 2019-11-14 manuscript/manuscript.Rmd
tables and figures temporarily rendered separate from the manuscript

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      #cache = TRUE,
                      fig.pos = 'H',
                      warning = FALSE,
                      message = FALSE)
```

@@

Large phenotypic differences were found between the sites by supervised random forest (Figure \@ref(fig:siteLocations))

@@

\newpage
## Tables

```{r tables,child='tables.Rmd'}
```

\newpage
## Figures

```{r figures,child='figures.Rmd'}
```

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      warning = FALSE,
                      message = FALSE)
```

@@

Large phenotypic differences were found between the sites by supervised random forest (Figure #)

@@

### 2019-11-14 manuscript/tables.Rmd
big rearrange
fixed file path changes
phenotypic descriptor info table added to plan
fixed descriptor table, site difference rf plot and DI space plot
supplementary now compiles
tables and figures temporarily rendered separate from the manuscript

```{r phenotypic_descriptors,cache=FALSE}
source('../code/phenotypic_descriptors.R')
pt %>%
  kable()
```

>>>>

---
title: Tables
output: pdf_document
---

## Tables

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      warning = FALSE,
                      message = FALSE)
```

```{r phenotypic_descriptors,cache=FALSE}
loadd(phenotypic_descriptor_info)

phenotypic_descriptor_info %>%
  kable(format = 'markdown')
```
